Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-03-01 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: more text

\begin{table*}[th]
\begin{tabular}{c | c c c c c c c c}
\hline
\hline
Theory & $p$ & $\delta \omega^{(0)}_{220}$ & $\delta \tau^{(0)}_{220}$ & $\delta \omega^{(1)}_{220}$ & $\delta \tau^{(1)}_{220}$ & QNM & Constraint & This work \\
\hline
sGB      & 4 & 0.0107 & 0.0044 & \dots & \dots &  \cite{Pierini:2021jxd} & $\ell_{\rm GB} \leqslant 1.18$~km~(GW)~\cite{Lyu:2022gdr} & \dots \\
dCS      & 4 & 3.1964 & 6.3619 & \dots & \dots &  \cite{Wagle:2021tam}   & $\ell_{\rm CS} \leqslant 8.5$~km~(EM+GW)~\cite{Silva:2020acr}  & \dots \\
cEFTofGR & 4 & $-0.3680$ $(-0.5131)$  & 1.9242 (1.7000) & \dots & \dots & \cite{Cano:2021myl} & --  & \dots \\
qEFTofGR & 6 & \dots & \dots & \dots & \dots & \cite{Cano:2021myl} & --  & \dots \\
\hline
\hline
\end{tabular}
\caption{Summary of the quasinormal modes calculations.
%
We summarize each theory we have considered together with: the exponent $p$ at
which their QNM-modification enters, the corresponding modifications to the
oscillation frequency $\delta \omega^{(i)}_{220}$ and decay time $\delta \tau^{(i)}_{220}$, the
references from which we used the results from and the current best constraint
(if applicable).
%
In the entries for cEFTofGR, the first entries in the $\delta
\omega^{(i)}_{220}$, $\delta \tau^{(i)}_{220}$ are obtained by considering
\emph{only parity-even corrections} and the second entries by considering
\emph{only parity-odd corrections}. In these cases, the dimensionless parameters
$\lambda_{\rm e,o}$ are degenerate with the length scale $\ell$.
%
\hs{Add a column with the constraint (if any) that we placed.}
\hs{TODO: add which runs are done and which need to be done.}
}
\label{tab:ref_theories_qnms}
\end{table*}

@@

There is a second criteria we must also consider.
%
As already emphasized in Ref.~\cite{Maselli:2019mjd}, the {\sc Parspec}
formalism is by construction perturbative. This means that the non-GR
deformation parameters are small, i.e.,
%
\begin{equation}
\gamma \, \delta \omega^{(j)} \ll 1 \,,
\quad \textrm{and} \quad
\gamma \, \delta \tau^{(j)} \ll 1 \,.
\end{equation}
%
for all $j$ of the expansion in dimensionless spin $\chi$.
%
We will also construct posterior distributions on the parameters and check if
most of their support is concentrated to a domain with values much smaller than
unity.

@@

\begin{figure}[t]
\includegraphics[width=\columnwidth]{figs/edgb_cdf_varying_threshold.pdf}
\caption{(Color online).~The cumulative distribution function evaluated at the
cut-off $\Lambda_{\rm EFT}(\varepsilon,\gm)$ EdGB gravity as a function of the parameter
$\varepsilon$ for both (blue curves) $m = m_2$, the secondary's source
mass, and (orange curves) $m = M_{f}$, the remnant's source mass, without
(solid curve) and with (dashed curves) linear in spin QNM corrections. The
horizontal lines lay at 0.68 and 0.90.
}
\label{fig:dcs_cdf}
\end{figure}

@@

\begin{figure}[t]
\includegraphics[width=\columnwidth]{figs/dcs_cdf_varying_threshold.pdf}
\caption{(Color online).~The cumulative distribution function evaluated at the cut-off $\Lambda_{\rm EFT}(\varepsilon, \gm)$
as a function of the parameter $\varepsilon$ for both (blue curves) $m = m_2$, the secondary's source mass,
and (orange curves) $m = M_{f}$, the remnant's source mass, without (solid curve) and with (dashed curves)
linear in spin QNM corrections. The horizontal lines lay at 0.68 and 0.90.
%
We see that the CDF at $\varepsilon = 1/2$ is approximately one when $\gm =
M_{f}$ for both events, with and without including the $j = 1$ dCS corrections
to the dominat QNM.
}
\label{fig:dcs_cdf}
\end{figure}

>>>>

\begin{table*}[th]
\begin{tabular}{c | c c c c c c c c}
\hline
\hline
Theory & $p$ & $\delta \omega^{(0)}_{220}$ & $\delta \tau^{(0)}_{220}$ & $\delta \omega^{(1)}_{220}$ & $\delta \tau^{(1)}_{220}$ & QNM & Constraint & This work \\
\hline
sGB      & 4 & 0.0107 & 0.0044 & \dots & \dots &  \cite{Pierini:2021jxd} & $\ell_{\rm GB} \leqslant 1.18$~km~(GW)~\cite{Lyu:2022gdr} & \dots \\
dCS      & 4 & 3.1964 & 6.3619 & \dots & \dots &  \cite{Wagle:2021tam}   & $\ell_{\rm CS} \leqslant 8.5$~km~(EM+GW)~\cite{Silva:2020acr}  & \dots \\
cEFTofGR & 4 & $-0.3680$ $(-0.5131)$  & 1.9242 (1.7000) & \dots & \dots & \cite{Cano:2021myl} & --  & \dots \\
qEFTofGR & 6 & \dots & \dots & \dots & \dots & \cite{Cano:2021myl} & --  & \dots \\
\hline
\hline
\end{tabular}
\caption{Summary of the quasinormal modes calculations.
%
We summarize each theory we have considered together with: the exponent $p$ at
which their QNM-modification enters, the corresponding modifications to the
oscillation frequency $\delta \omega^{(i)}_{220}$ and decay time $\delta \tau^{(i)}_{220}$, the
references from which we used the results from and the current best constraint
(if applicable).
%
In the entries for cEFTofGR, the first entries in the $\delta
\omega^{(i)}_{220}$, $\delta \tau^{(i)}_{220}$ are obtained by considering
\emph{only parity-even corrections} and the second entries by considering
\emph{only parity-odd corrections}. In these cases, the dimensionless parameters
$\lambda_{\rm e,o}$ are degenerate with the length scale $\ell$.
%
% \hs{Add a column with the constraint (if any) that we placed.}
% \hs{TODO: add which runs are done and which need to be done.}
}
\label{tab:ref_theories_qnms}
\end{table*}

@@

There is a second criteria we must also consider.
%
As already emphasized in Ref.~\cite{Maselli:2019mjd}, the {\sc Parspec}
formalism is by construction perturbative. This means that the non-GR
deformation parameters are small, i.e.,
%
\begin{equation}
\gamma \, \delta \omega^{(j)} \ll 1 \,,
\quad \textrm{and} \quad
\gamma \, \delta \tau^{(j)} \ll 1 \,.
\label{eq:parspec_bound}
\end{equation}
%
for all $j$ of the expansion in dimensionless spin $\chi$.
%
We will also construct posterior distributions on the parameters and check if
most of their support is concentrated to a domain with values much smaller than
unity.

@@

\begin{figure}[t]
\includegraphics[width=\columnwidth]{figs/edgb_cdf_varying_threshold.pdf}
\caption{(Color online).~The cumulative distribution function evaluated at the
cut-off $\Lambda_{\rm EFT}(\varepsilon,\gm)$ EdGB gravity as a function of the parameter
$\varepsilon$ for both (blue curves) $\gm = m_2$, the secondary's source
mass, and (orange curves) $\gm = M_{f}$, the remnant's source mass, without
(solid curve) and with (dashed curves) linear in spin QNM corrections. The
horizontal lines lay at 0.68 and 0.90.
}
\label{fig:dcs_cdf}
\end{figure}

@@

\begin{figure}[t]
\includegraphics[width=\columnwidth]{figs/dcs_cdf_varying_threshold.pdf}
\caption{(Color online).~The cumulative distribution function evaluated at the cut-off $\Lambda_{\rm EFT}(\varepsilon, \gm)$
as a function of the parameter $\varepsilon$ for both $\gm = m_2$ (blue curves), the secondary's source mass,
and $\gm = M_{f}$ (orange curves), the remnant's source mass, without (solid curve) and with (dashed curves)
linear in spin QNM corrections. The horizontal lines lay at 0.68 and 0.90.
%
We see that the CDF at $\varepsilon = 1/2$ is approximately one when $\gm =
M_{f}$ for both events, with and without including the $j = 1$ dCS corrections
to the dominat QNM.
}
\label{fig:dcs_cdf}
\end{figure}

\begin{table}[h]
\begin{tabular}{l l c c c}
\hline
\hline
Event & $j$ & Eq.~\eqref{eq:eft_bound}? & Eq.~\eqref{eq:parspec_bound}?  & Bound \\
\hline
GW150914 & $j = 0$    & Yes & Yes & $\ell_{\rm CS} \leqslant \dots$~km \\
GW150914 & $j = 0, 1$ & Yes & No  & --                                 \\
GW200129 & $j = 0$    & Yes & Yes & $\ell_{\rm CS} \leqslant \dots$~km \\
GW200129 & $j = 0, 1$ & Yes & No  & --                                 \\
\hline
\hline
\end{tabular}
\caption{Detailed summary of our results for dCS gravity.
%
We assume $\varepsilon = 1/2$.}
\end{table}
